\pkg{partykit}: A Modular Toolkit for Recursive Partytioning in \proglang{R}

### 2015-02-20 pkg/partykit/inst/mloss/mloss2.Rnw
added cforest comment in discussion, updated references
git-svn-id: svn://svn.r-forge.r-project.org/svnroot/partykit@687 255f4249-2263-4417-b1ea-8498779e27a7

%% header declarations
\author{Torsten Hothorn \\ \addr{Universit\"at Z\"urich} \\ \addr{E-mail: Torsten.Hothorn@R-project.org} \AND
        Achim Zeileis \\ \addr{Universit\"at Innsbruck} \\ \addr{E-mail: Achim.Zeileis@R-project.org}}
\title{\pkg{partykit}: A Modular Toolkit for Recursive Partytioning in \proglang{R}}
\editor{Cheng Soon Ong (MLOSS track, JMLR-14-133)}

@@

Package \pkg{partykit} provides a toolkit for trees in \proglang{R} that gives
emphasis to flexibility and extensibility. The infrastructure is easily
accessible and accompanied by detailed manual pages and package vignettes.
The package facilitates the implementation of new algorithms or interfacing
other software by providing common building blocks for computing on trees
(representation, printing, plotting, predictions, etc.). Using these building
blocks developers of tree software can focus on implementing the learning
algorithm (selection of variables and split points, stopping criteria, pruning, etc.).
The package also provides functions for inferring trees where the computationally
intensive parts are either in \proglang{C} (\fct{ctree}) or employ \proglang{R}'s
fitting functions (\fct{mob}). The simple and lean base classes that separate
data and tree structure are also appealing for storing forests which are planned
for future versions of the package. Users and developers that have questions or
comments about the package can either contact the maintainers or use the forum
on \proglang{R}-Forge at \url{https://R-Forge.R-project.org/forum/forum.php?forum_id=852}.

>>>>

%% header declarations
\author{Torsten Hothorn \\ \addr{Universit\"at Z\"urich} \\ \addr{E-mail: Torsten.Hothorn@R-project.org} \AND
        Achim Zeileis \\ \addr{Universit\"at Innsbruck} \\ \addr{E-mail: Achim.Zeileis@R-project.org}}
\title{\pkg{partykit}: A Modular Toolkit for Recursive Partytioning in \proglang{R}}
\editor{Cheng Soon Ong}

@@

Package \pkg{partykit} provides a toolkit for trees in \proglang{R} that gives
emphasis to flexibility and extensibility. The infrastructure is easily
accessible and accompanied by detailed manual pages and package vignettes.
The package facilitates the implementation of new algorithms or interfacing
other software by providing common building blocks for computing on trees
(representation, printing, plotting, predictions, etc.). Using these building
blocks developers of tree software can focus on implementing the learning
algorithm (selection of variables and split points, stopping criteria, pruning, etc.).
The package also provides functions for inferring trees where the computationally
intensive parts are either in \proglang{C} (\fct{ctree}) or employ \proglang{R}'s
fitting functions (\fct{mob}). The simple and lean base classes that separate
data and tree structure are also appealing for storing forests -- a first proof-of-concept
reimplementation of \fct{cforest} is in the package with further extension planned.
Users and developers that have questions or comments about the package can either
contact the maintainers or use the forum
on \proglang{R}-Forge at \url{https://R-Forge.R-project.org/forum/forum.php?forum_id=852}.
